Unimodular covers of 3-dimensional parallelepipeds and Cayley sums

### 2023-01-08 JCOMB-reports/response to referees.txt

We have carefully gone through all the (very helpful and detailed) suggestions of both referees and we have implemented almost all of them. Below is a response explaining what we did:

Response to referee X
---------------------
1-7: agreed and corrected.
8: we are aware that the proof of Lemma 3.2 is complicated. This is why we put it in its own section 4, and in section 3 we use Lemma 3.2 as a black-box to prove Theorem 1.6. We are not sure what kind of example we could/should put.
9: agreed and corrected.
10: we have rephrased in a hopefully clearer way.
11: we have hopefully solved this too. In particular, the proofs of Claims 4.2, 4.3 and the conclusion after 4.4 have been edited and clarified.

Response to referee Y
---------------------
1: agreed & changed
2: added definition of Minkowski sum where it is first used (in the definition of IDP-ness).
3-9: agreed & changed
10: here the referee seems not to notice that the points q_i are not necessarily lattice points. We have added a line to this effect.
11-15: agreed & changed
16: this would be another way to go, but we have decided to keep the original formulation
17-23: agreed & changed
24: added a line in the explanation above lemma 3.2 explaining that the prod-simplices we are interested in are sums of segments, ie. parallelograms
25-30: agreed & changed
31: in the text we never make the assumption that the segments p and q are vertical and horizontal. We just draw them that way and use the letters $V$ and $H$ for the half-planes that they define for convenience. And, anyway, p and q can be made vertical and horizontal via a linear transformation (which of course changes the lattice, but is not a problem here. The proof never assumes the lattice to be the integers). We have added a sentence to this effect before Figure 3.2, which already shows $p$ and $q$ as vertical and horizontal.
32-38: agreed & changed
39: see our comment to 31. What may actually be misleading is that in some of our pictures the lattice still looks orthogonal (that is, having a square fundamental domain), but that fact is never used in the proofs, which are totally "affine".
40: thank you! There was a sign mistake, with a "-1" instead of "+1" in the equation of g the inequalities are now correct.
41: agreed & changed
42-43: the conclusion of the proof of lemma 3.2 has been edited for clarity and to correct the mistake from comment 40.

### 2023-01-08 unimodular-covers-CombTheory-reviewing.tex
minor edits. changed name of response file

Oda \cite{Oda1997} posed several questions regarding smoothness and the IDP property for lattice polytopes.
%
Following \cite{HaaseHof, Tsuchiya}, we say that a pair $(P, Q)$ of lattice polytopes has the integer decomposition property, or that \emph{the pair $(P,Q)$ is IDP}, if 
\begin{align*}
\label{eq:mixedIDP}
(P+Q) \cap \Z^d = P \cap \Z^d + Q \cap \Z^d,
\end{align*}
where $A+B :=\{a+b: a\in A, b\in B\}$ denotes the \emph{Minkowski sum} of two sets $A,B\subset \R^d$.

@@

More explicitly, the the remaining vertices $q_i$ of the circumscribed parallelepiped are $(\frac{a+1}{2}, \frac{b+1}{2}, 1), (\frac{a+1}{2}, \frac{b+1}{2}, 0), (\frac{1-a}{2}, \frac{b-1}{2}, 1), (\frac{a-1}{2}, \frac{1-b}{2}, 1)$. None of these points are contained in $P$, and therefore none of the corner tetrahedra are either.
\end{example}
%\giulia{Added the last part to answer comment Y.19}

@@

Indeed, in both cases the 
%only lattice points are the six vertices and the origin. The 
point $(1,1,1)$ lies in the second dilation but is not the sum of two lattice points in the polytope. 
%Hence, they are not IDP, which implies they do not admit unimodular covers.
\end{example}

@@

\begin{proposition}[see, e.g.~\protect{\cite[Thm.~0.4]{Tsuchiya}}]
\label{prop:mixedIDP}
If $\cayley(P,Q)$ is IDP then the pair $(P,Q)$ is IDP.
\end{proposition} 
%\giulia{We just called the pair IDP in the introduction... Which notation do we prefer?}

>>>>

Oda \cite{Oda1997} posed several questions regarding smoothness and the IDP property for lattice polytopes.
%
Following \cite{HaaseHof, Tsuchiya}, we say that a pair $(P, Q)$ of lattice polytopes has the integer decomposition property, or that \emph{the pair $(P,Q)$ is IDP}, if 
\begin{align*}
\label{eq:mixedIDP}
(P+Q) \cap \Z^d = P \cap \Z^d + Q \cap \Z^d,
\end{align*}
where $A+B :=\{a+b: a\in A, b\in B\}$ denotes the \emph{Minkowski sum} of two sets $A,B\subset \R^d$.
\paco{added def of Minkowski sum}

@@

More explicitly, the the remaining vertices $q_i$ of the circumscribed parallelepiped are $(\frac{a+1}{2}, \frac{b+1}{2}, 1), (\frac{a+1}{2}, \frac{b+1}{2}, 0), (\frac{1-a}{2}, \frac{b-1}{2}, 1), (\frac{a-1}{2}, \frac{1-b}{2}, 1)$. None of these points are contained in $P$, and therefore none of the corner tetrahedra are either.
\giulia{Added the last part to answer comment Y.19}
\paco{edited it}
\end{example}

@@

Indeed, in both cases the 
\paco{shortened}
point $(1,1,1)$ lies in the second dilation but is not the sum of two lattice points in the polytope. 
\end{example}

@@

\begin{proposition}[see, e.g.~\protect{\cite[Thm.~0.4]{Tsuchiya}}]
\label{prop:mixedIDP}
If $\cayley(P,Q)$ is IDP then the pair $(P,Q)$ is IDP.
\end{proposition} 
\giulia{We just called the pair IDP in the introduction... Which notation do we prefer?}
\paco{we stick to just IDP}
